---
title: "Open Grants PDF Ingestion on Elasticsearch"
author: "Daniel Nüst"
date: "9/2/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = FALSE)
```

This document is not intended to be knitted as full, but to document a step-by-step process.
Therefore chunks are not evaluated by default.

Using the [`elastic`](https://docs.ropensci.org/elastic/) R package.

```{r libraries}
library("elastic")
```

## Start local Elasticsearch

From the root of the `ogrants` project, run

```bash
docker build --tag ogrants .
docker run -p 9200:9200 -p 9300:9300 -e "discovery.type=single-node" ogrants
```

## Connect

```{r connect}
es <- connect()
```

## Set up ingest pipeline

- https://www.elastic.co/guide/en/elasticsearch/plugins/current/using-ingest-attachment.html
- https://stackoverflow.com/questions/37861279/how-to-index-a-pdf-file-in-elasticsearch-5-0-0-with-ingest-attachment-plugin
- https://docs.ropensci.org/elastic/reference/ingest.html

We want the following as R command:

```bash
PUT _ingest/pipeline/attachment
{
  "description" : "Extract attachment information",
  "processors" : [
    {
      "attachment" : {
        "field" : "data",
        "indexed_chars" : -1
      }
    }
  ]
}
```

```{r pipeline}
boddy <- '{
  "description" : "Extract attachment information",
  "version" : 1,
  "processors" : [
    {
      "attachment" : {
        "field": "fulltext",
        "indexed_chars" : -1
      }
    }
  ]
}'
pipeline_create(es, id = 'pdfin', body = boddy)

body_attach <- '{
  "fulltext": "e1xydGYxXGFuc2kNCkxvcmVtIGlwc3VtIGRvbG9yIHNpdCBhbWV0DQpccGFyIH0="
}'

if (!index_exists(es, "ogrants")) index_create(es, "ogrants")
docs_create(es, "ogrants", id = 1, body = list(title = "New title"))

pipeline_attachment(es, index = "ogrants", id = "1", pipeline = "pdfin", body_attach)
pipeline_get(es, id = "pdfin")
```
```{r pipeline2}
pipeline_get(es, "pdfin")
```
```{r pipeline2}
docs_get(es, index = "ogrants", id = 1)
```

## Get example PDF

See ogrants repo.

## Convert ogrants record into JSON

1. read yaml header with `yaml`
2. read PDF as base64
3. construct requests (see above) to create doc and attachment
4. query document - the full text should be in a plain text field

## Some local example queries

### from a URL to a pdf, create a document

```{r helper function to construct body}
make_body_attach <- function(binary_dat)
{
  paste0('{\n  "fulltext": "', base64enc::base64encode(binary_dat), '"\n}')
}
```

```{r deposit sample pdf}
# retrieve sample pdf
link <- "https://www.niaid.nih.gov/sites/default/files/K01-Lilliam-Ambroggio-Application.pdf"
resp <- httr::GET(link)
binary_dat <- httr::content(resp, "raw")
body_attach <- make_body_attach(binary_dat)

# create a document and attach data
docs_create(es, "ogrants", id = 2, body = list(title = "New title"))
pipeline_attachment(es, index = "ogrants", id = "2", pipeline = "pdfin", body_attach)
```

```{r check status of sample pdf}
status <- docs_get(es, index = "ogrants", id = 2)
str(status)
```



## Connect to online ES instance

Set up credentials in `.Renviron` file for this project with `usethis::edit_r_environ("project"); Sys.chmod(".Renviron", mode = "0400")`.
Then you can read the ID and KEY from the environment variables.

[If we want to share passwords more securely in the future, try out [`keyring`](https://cran.r-project.org/web/packages/httr/vignettes/secrets.html).]

```{r passwords}
#Sys.getenv("OGRANTS_ES_USER_READ_ID")
#Sys.getenv("OGRANT_ES_USER_READ_KEY")
id = Sys.getenv("OGRANTS_ES_USER_FULL_ID")
key = Sys.getenv("OGRANTS_ES_USER_FULL_KEY")
```

- https://docs.aws.amazon.com/elasticsearch-service/latest/developerguide/es-gsg-upload-data.html
- https://docs.aws.amazon.com/elasticsearch-service/latest/developerguide/es-ac.html

```{r connect_public}
library("elastic")
es <- connect(host = "search-open-grants-vac5xkmdgahhvqfohcmkvxrysa.eu-west-1.es.amazonaws.com", user = id, pwd = key, transport_schema = "http")

elastic::cat_(conn = es)
elastic::Search(es, q = "test")

elastic::nodes_info(es)
```

