---
title: "Open Grants PDF Ingestion on Elasticsearch"
author: "Daniel Nüst"
date: "9/2/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = FALSE)
```

This document is not intended to be knitted as full, but to document a step-by-step process.
Therefore chunks are not evaluated by default.

Using the [`elastic`](https://docs.ropensci.org/elastic/) R package.

```{r libraries}
library("elastic")
```

## Start local Elasticsearch

From the root of the `ogrants` project, run

```bash
docker build --tag ogrants .
docker run -p 9200:9200 -p 9300:9300 -e "discovery.type=single-node" ogrants
```

## Connect

```{r connect}
es <- connect()
```

## Set up ingest pipeline

- https://www.elastic.co/guide/en/elasticsearch/plugins/current/using-ingest-attachment.html
- https://stackoverflow.com/questions/37861279/how-to-index-a-pdf-file-in-elasticsearch-5-0-0-with-ingest-attachment-plugin
- https://docs.ropensci.org/elastic/reference/ingest.html

We want the following as R command:

```bash
PUT _ingest/pipeline/attachment
{
  "description" : "Extract attachment information",
  "processors" : [
    {
      "attachment" : {
        "field" : "data",
        "indexed_chars" : -1
      }
    }
  ]
}
```

```{r pipeline}
boddy <- '{
  "description" : "Extract attachment information",
  "version" : 1,
  "processors" : [
    {
      "attachment" : {
        "field": "fulltext",
        "indexed_chars" : -1
      }
    }
  ]
}'
pipeline_create(es, id = 'pdfin', body = boddy)

body_attach <- '{
  "fulltext": "e1xydGYxXGFuc2kNCkxvcmVtIGlwc3VtIGRvbG9yIHNpdCBhbWV0DQpccGFyIH0="
}'

if (!index_exists(es, "ogrants")) index_create(es, "ogrants")
docs_create(es, "ogrants", id = 1, body = list(title = "New title"))

pipeline_attachment(es, index = "ogrants", id = "1", pipeline = "pdfin", body_attach)
pipeline_get(es, id = "pdfin")
```
```{r pipeline2}
pipeline_get(es, "pdfin")
```
```{r pipeline2}
docs_get(es, index = "ogrants", id = 1)
```

## Get example PDF

See ogrants repo.

## Convert ogrants record into JSON

1. read yaml header with `yaml`
2. read PDF as base64
3. construct requests (see above) to create doc and attachment
4. query document - the full text should be in a plain text field

## Some local example queries

### from a URL to a pdf, create a document

```{r helper function to construct body}
make_body_attach <- function(binary_dat)
{
  paste0('{\n  "fulltext": "', base64enc::base64encode(binary_dat), '"\n}')
}
```

```{r deposit sample pdf}
# retrieve sample pdf
link <- "https://www.niaid.nih.gov/sites/default/files/K01-Lilliam-Ambroggio-Application.pdf"
resp <- httr::GET(link)
binary_dat <- httr::content(resp, "raw")
body_attach <- make_body_attach(binary_dat)

# create a document and attach data
docs_create(es, "ogrants", id = 2, body = list(title = "New title"))
pipeline_attachment(es, index = "ogrants", id = "2", pipeline = "pdfin", body_attach)
```

```{r check status of sample pdf}
status <- docs_get(es, index = "ogrants", id = 2)
str(status)
```



## Connect to online ES instance

Set up credentials in `.Renviron` file for this project with `usethis::edit_r_environ("project"); Sys.chmod(".Renviron", mode = "0400")`.
Then you can read the ID and KEY from the environment variables.

[If we want to share passwords more securely in the future, try out [`keyring`](https://cran.r-project.org/web/packages/httr/vignettes/secrets.html).]

- https://docs.aws.amazon.com/elasticsearch-service/latest/developerguide/es-gsg-upload-data.html
- https://docs.aws.amazon.com/elasticsearch-service/latest/developerguide/es-ac.html

```{r connect_public}
library("elastic")

id_pub <- Sys.getenv("OGRANTS_ES_USER_READ_ID")
key_pub <- Sys.getenv("OGRANT_ES_USER_READ_KEY")

scheme <- "https"
# the following results in a connection refused error > need signing
es_pub <- connect(host = "search-open-grants-vac5xkmdgahhvqfohcmkvxrysa.eu-west-1.es.amazonaws.com",
                  port = "443", transport_schema = scheme,
                  user = id_pub, pwd = key_pub)
elastic::cat_(conn = es_pub)
```

- helper package from cloudyr project > https://cran.r-project.org/web/packages/aws.signature/
- https://docs.aws.amazon.com/elasticsearch-service/latest/developerguide/es-request-signing.html
- endpoint: https://search-open-grants-vac5xkmdgahhvqfohcmkvxrysa.eu-west-1.es.amazonaws.com/_cat

```{r connect_signed}
# install.packages("aws.signature", repos = c(cloudyr = "http://cloudyr.github.io/drat", getOption("repos")))
library("aws.signature")
library("httr")

es_request <- function(server = "search-open-grants-vac5xkmdgahhvqfohcmkvxrysa",
                       key,
                       secret,
                       verb = "GET",
                       action = "/_search",
                       query = list(`q` = "*"),
                       service = "es",
                       region = "eu-west-1",
                       headers = c(),
                       body = "") {
  # following lines based on https://github.com/cloudyr/aws.alexa/blob/b421fca047c9d22d2b2e645e9052c45daa7e57fe/R/aws.alexa.package.R
  hostname <- paste0(server, ".", region, ".", service, ".amazonaws.com")
  current <- Sys.time()
  header_timestamp <- format(current, "%Y-%m-%dT%H:%M:%SZ", tz = "UTC")
  canonical_headers <- c(list(host = hostname,
                              `x-amz-date` = header_timestamp),
                         headers)

  Sig <- signature_v4_auth(datetime = format(current, "%Y%m%dT%H%M%SZ", tz = "UTC"),
                           region = region,
                           service = service,
                           verb = verb,
                           action = action,
                           query_args = query,
                           canonical_headers = canonical_headers,
                           request_body = body,
                           key = key,
                           secret = secret,
                           session_token = NULL,
                           verbose = TRUE)

  headers <- c(headers,
               `x-amz-date` = header_timestamp,
               `x-amz-content-sha256` = Sig$BodyHash,
               #if (!is.null(session_token) && session_token != "") { headers[["x-amz-security-token"]] <- session_token }
               `Authorization` = Sig[["SignatureHeader"]])

  browser()
  res <- httr::RETRY(verb = verb,
                     url = httr::modify_url(url = hostname, scheme = scheme, hostname = hostname, path = action),
                     httr::add_headers(headers),
                     query = query,
                     times = 3,
                     terminate_on = c(403, 404),
                     terminate_on_success = TRUE)
  res
}

library("crul")
es_request_crul <- function(conn,
                            # TODO: get server, service, and region from the connection object?
                            server = "search-open-grants-vac5xkmdgahhvqfohcmkvxrysa",
                            verb = "GET",
                            action = "/_search",
                            query = list(`q` = "*"),
                            service = "es",
                            region = "eu-west-1",
                            headers = c(),
                            body = "") {
  # following lines based on https://github.com/cloudyr/aws.alexa/blob/b421fca047c9d22d2b2e645e9052c45daa7e57fe/R/aws.alexa.package.R
  hostname <- paste0(server, ".", region, ".", service, ".amazonaws.com")
  current <- Sys.time()
  header_timestamp <- format(current, "%Y-%m-%dT%H:%M:%SZ", tz = "UTC")
  canonical_headers <- c(list(host = hostname,
                              `x-amz-date` = header_timestamp),
                         headers)

  Sig <- signature_v4_auth(datetime = format(current, "%Y%m%dT%H%M%SZ", tz = "UTC"),
                           region = region,
                           service = service,
                           verb = verb,
                           action = action,
                           query_args = query,
                           canonical_headers = canonical_headers,
                           request_body = body,
                           key = conn$user,
                           secret = conn$pwd,
                           session_token = NULL,
                           verbose = TRUE)

  headers <- c(headers,
               `x-amz-date` = header_timestamp,
               `x-amz-content-sha256` = Sig$BodyHash,
               #if (!is.null(session_token) && session_token != "") { headers[["x-amz-security-token"]] <- session_token }
               `Authorization` = Sig[["SignatureHeader"]])

  # based on https://github.com/ropensci/elastic/blob/03177398be3f6d1d4991f9796794bfe0380d56d0/R/httr-verbs.R#L26
  # TODO add option to use body, see function check_iputs in above script
  browser()
  client <- crul::HttpClient$new(
    #url = httr::modify_url(url = hostname, scheme = scheme, hostname = hostname, path = action),
    url = paste0(conn$make_url(), action),
    headers = c(conn$headers, headers),
    opts = conn$opts)
  res <- client$verb(verb = "retry",
                     verb,
                     query = query,
                     times = 3,
                     terminate_on = c(403, 404)
                     )
  elastic:::geterror(conn, res)
  jsonlite::fromJSON(tt$parse("UTF-8"), FALSE)
}
```

```{r request_public}
response <- es_request(key = id_pub, secret = key_pub, query = list(`q` = "test"))
httr::content(response)
```
Works!

```{r request_public_crul}
response <- es_request_crul(conn = es_pub)
response
```

```{r request_full}
id = Sys.getenv("OGRANTS_ES_USER_FULL_ID")
key = Sys.getenv("OGRANTS_ES_USER_FULL_KEY")

es <- connect(host = "search-open-grants-vac5xkmdgahhvqfohcmkvxrysa.eu-west-1.es.amazonaws.com",
              port = "443", transport_schema = "https",
              user = id, pwd = key)

elastic::cat_(conn = es)
elastic::Search(es, q = "test")

elastic::nodes_info(es)
```

